### 2021-02-11 cover_letter.tex
lots of rewrites for a more positive spin and more compact wording

\noindent This paper is a resubmission of JMLR manuscript 20-416.  We were
encouraged to resubmit a revised article after addressing the comments of the
reviewers; now that we have addressed each comment, we are ready to submit our
revision.  We hope that you find our updates satisfactory. \\

\noindent Below is a summary of changes:

\begin{itemize}
  \item Following the comments from Reviewer 1, we agree that Table 1 is
confusing, and we have simply removed it.  This allows more space for
experiments.

  \item To demonstrate the utility and efficiency of ensmallen on real-world
problems, we added an experiment comparing ensmallen to other toolkits to train
a logistic regression model on real-world datasets from the UCI dataset
repository.  Unfortunately, with only four pages, we were unable to figure out
how to include any more experiments in the given space.  Readers who are
interested in more information could refer to a few additional experiments in
the technical report that is referenced at the end of the conclusion.

  \item We also added PyTorch and TensorFlow to the list of competitors for our
experiments.

  \item We were concerned by the report of test failures by Reviewer 1 (thank
you for the report!).  Many tests in ensmallen are probabilistic---we choose a
random initial point, then ensure that the optimizer is able to reach somewhere
close to the expected minimum.  Convergence is not always guaranteed, so
sometimes we must run a handful of trials.  We overhauled our test
infrastructure such that we are now able to run our tests 1000 times with
different random seeds and no failures.  (Our changes can be seen in
\url{https://github.com/mlpack/ensmallen/pull/249}.)  This revamped test suite
is a part of the latest release, ensmallen 2.15.2.

  \item Following the suggestion of Reviewer 1, we added a simple test example
in the root of the repository ({\tt example.cpp}), and a link to it from the
ensmallen documentation at \url{https://ensmallen.org/docs.html}.  We agree that
this is a nice improvement; thanks to Reviewer 1 for suggesting this change.
\end{itemize}

\noindent We are always interested in more opportunities to improve our work,
and so we look forward to additional feedback. \\

\noindent Thank you!

>>>>

\noindent This paper is a resubmission of JMLR manuscript 20-416.  We were
encouraged to resubmit a revised article after addressing the reviewers' comments.
Below is a summary of the changes:

\begin{itemize}
  \item Following the comments from Reviewer 1, we agree that Table 1 is
confusing. We have removed it.  This has opened up space to provide an extra experiment.

  \item To demonstrate the utility and efficiency of {\it ensmallen} on real-world
problems, we added an experiment comparing {\it ensmallen} to other toolkits in the context of training 
a logistic regression model on real-world datasets from the UCI dataset
repository.  While we would like to add even more experiments,
we are constrained by the four page limit for this manuscript.
However, additional experiments for interested readers are given
in the accompanying technical report, which is cited at the end of the conclusion.

  \item As per the suggestion of Reviewer 1, we added PyTorch and TensorFlow
  for comparison in our experiments.

  \item We have addressed the test failures reported by Reviewer 1.
Many tests in {\it ensmallen} are probabilistic, where a random initial point is used,
followed by checking that an optimizer is able to reach somewhere
close to the expected minimum.  However, given the nature of many optimizers,
convergence to an expected point is not always guaranteed.
To address this, we overhauled our test infrastructure such that we are now able
to run our tests 1000 times with unique random seeds and no failures.
The revamped test suite is part of the latest release, ensmallen 2.15.2.
(The changes can be viewed in \url{https://github.com/mlpack/ensmallen/pull/249}).

  \item Following the suggestion of Reviewer 1, we added a simple example program
in the root of the repository ({\tt example.cpp}), and added a link to it from the
ensmallen documentation at \url{https://ensmallen.org/docs.html}.
The example program is indeed very useful for newcomers.
\end{itemize}

\noindent We would like to thank the reviewers for their constructive feedback,
which has been very useful for improving both the software and the manuscript.
